Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-07-20 articles/formalism/sections/real_space_formalism.tex
Minor edits through 3.4

which are the real space analogues of their harmonic space counterparts discussed in \sec{sec:mat_pol_intro}. Thus they are exactly orthogonal and idempotent. Note that unlike in the harmonic case, the sum of the operators is the band limited identity operator $\mathcal{I}$. This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit. Forcing the sum of the operators to be exactly an identity matrix compromises the orthogonality property of the $\bar{O}_E$ \& $\bar{O}_B$ operators which is exact (\eq{eq:real_ortho}) and a more crucial property of the operators.

>>>>

which are the real space analogues of their harmonic space counterparts discussed in \sec{sec:mat_pol_intro}. Thus they are exactly orthogonal and idempotent. Note that unlike in the harmonic case, the sum of the operators is the band limited identity operator $\mathcal{I}$. This non-exactness is representative of the loss of information resulting from making this transformation on measured data with some imposed band limit. If we were to force the sum of the operators to be exactly an identity matrix, we would compromise the orthogonality property of $\bar{O}_E$ and $\bar{O}_B$, which is exact (\eq{eq:real_ortho}) and a more crucial property of the operators.
